%Here is all the information about the hardware
The hardware is built to exceed the requirement for the current motor and also be able to control more powerful equipment with a bit of safety margin. \newline
The hardware is built up by 2 H-bridges, sharp 2Y0A21F IR snesor, NI myRIO, 42BYGHM809 Bipolar stepper motor and a LM2596 DC-DC buck converter. 
Each H-bridge have a pair of high power N and P MOSFETs (2 of each) which need 10V to open.\newline
4 optocouplers provide the MOSFETs with a high voltage line (of 10+V) to open since the voltage to the stepper motor is only 3.3V and the myRIO can't open the MOSFET by itself. The optocouplers also provide galvanic isolation between the expensive myRIO and the high power motor control. 
Between the optocouplers and MOSFETs there is a pull-up and pull-down resistors to give a safe off state and clean signal.\newline
Each P-MOSFET have a pull-up resistor from gate to the 10+V MOSFET supply giving it a reliable 10+V reference for it to remain closed. The optocoupler to that MOSFET sits between gate and ground and then ground the P-MOSFET when activated and in turn opening the P-MOSFET.\newline
Comparably each N-MOSFET have a pull-down resistor between gate and ground for a grounded (closed) off state. Opposite the P-MOSFET the optocoupler for the N-MOSFET sits between the MOSFET supply voltage and gate, supplies the N-MOSFET with voltage when activated and in turn opnening the N-MOSFET.\newline
On the digital side of the optocoplers (where the myRIO is connected) there is a 75$\Omega$ after each optocoupler for current limitation. The myRIO can only output 3mA (on multiple DO pins simultaneous) but with absolutely no limitation outside that the myRIOs over current protection would kick in. 75$\Omega$ is enough to prevent over current but the more suitable 1100$\Omega$ limiter resistor (calculated for 3mA at 3,3V) that was planned never arrived.\newline
High power motors also create a lot of noise and therefor there is two pairs of capacitors. One 100$\mu$ F and one smaller 1$\mu$ F to smooth out different types of noise. There is one pair of capacitors on each power line (motor power and MOSFET power).